Local-to-Global Mariculture Modelling

### 2025-12-15 docs-working/07_how_many_runs_per_farm.qmd
Updates

# Get a small but representative sample
samp <- ts_means %>%
  mutate(temp_bin = ntile(mean, 15)) %>%
  group_by(temp_bin) %>%
  slice_sample(n = 2) %>%
  ungroup() %>%
  pull(farm_ID)

>>>>

# Get a small sample
samp <- ts_means %>%
  mutate(temp_bin = ntile(mean, 15)) %>%
  group_by(temp_bin) %>%
  slice_sample(n = 2) %>%
  ungroup() %>%
  pull(farm_ID)

### 2025-12-15 docs-working/index.qmd
Updates

---
title: "Local-to-Global Mariculture Modelling"
subtitle: "Project Documentation"
author: "Dr Tormey Reimer"
date: today
execute:
  eval: true
  echo: false
  warning: false
  message: false
  cache: true # quarto render index.qmd --cache-refresh
knitr: 
  opts_chunk:
    fig.align: center
    fig.width: 8.5
format:
  html:
    code-fold: true
---

>>>>

---
title: "Local-to-Global Mariculture Modelling"
subtitle: "Project Documentation"
author: "Dr Tormey Reimer"
date: today
execute:
  # eval: true
  echo: false
  warning: false
  message: false
  cache: true # quarto render index.qmd --cache-refresh
knitr: 
  opts_chunk:
    fig.align: center
    fig.width: 8.5
format:
  html:
    code-fold: true
---
